Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

\ReviewerThree{The time courses contain oscillations due to the
granularity of the JP vesicle.
The curve for $\chi = 0.003$ in Figure~\ref{figure4}a, for example, 
has a low-frequency oscillation with a period around $0.7$ $\upmu$s,
and a high-frequency oscillation with a period four times smaller.
The JP vesicle is somewhat hexagonal (see, e.g., Figure~\ref{figure5}a)
and the low-frequency oscillations corresponds to the tank-treading of a 
polygon, rather than smooth, curve. The higher frequency oscillations
comes from the trank-treading of individual particles, that is
it corresponds to the rate of passage of particles through a fixed-angle
axis about the vesicle centre.} 
The inset of Figure~\ref{figure4}c zooms
in on the arc length data for the shear rate $\chi = 0.003$. It shows
that the curves are smooth and well-resolved by our second-order
Adams-Bashforth scheme.

>>>>

\ReviewerThree{The time courses contain oscillations due to the
granularity of the JP vesicle.
The curve for $\chi = 0.003$ in Figure~\ref{figure4}a, for example, 
has a low-frequency oscillation with a period around $0.7$ $\upmu$s,
and a high-frequency oscillation with a period four times smaller.
The JP vesicle is somewhat hexagonal (see, e.g., Figure~\ref{figure5}a)
and the low-frequency oscillations corresponds to the tank-treading of a 
polygon, rather than smooth, curve. The higher frequency oscillations
come from the trank-treading of individual particles, that is
they correspond to the rate of passage of particles through a fixed-angle
axis about the vesicle centre.} 
The inset of Figure~\ref{figure4}c zooms
in on the arc length data for the shear rate $\chi = 0.003$. It shows
that the curves are smooth and well-resolved by our second-order
Adams-Bashforth scheme.
